Estimating the genome-wide contribution of selection to temporal allele frequency change

### 2020-04-18 manuscript/manuscript.tex
updated ms

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/fig-bgs-G.pdf}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/fig-bgs-covars.pdf}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/fig-bgs-}

>>>>

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/fig-bgs-G-without-fixations.pdf}

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/fig-bgs-covars-without-fixations.pdf}

@@

In analyzing both the empirical datasets included in our study and our
simulation results, we noticed the temporal covariances and $G(t)$ statistics
are sensitive to how fixations are handled. Through simulations and comparing
the results of analyzing our empirical datasets both ways, we have found
tradeoffs to both approaches, but overall not removing fixed sites is a more
conservative, safer approach, and is what we use throughout our paper.

Temporal covariances (and related statistics like convergence correlations,
$G(t)$, etc.) are calculated on allele frequency changes, $\Delta p_t$; when an
allele is fixed or lost, the allele frequency changes are zero thereafter
$\Delta p_t = 0$. When temporal covariance is calculated by averaging over the
loci in a region or across the genome, fixed sites zero out the terms in the
sum of the right hand side of temporal covariance, $\cov(\Delta p_t, \Delta
p_s) = \E(\Delta p_t \Delta p_s) - \E(\Delta p_t) \E(\Delta p_s)$ and can
shrink the second terms towards zero.

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/fig-bgs-G-with-fixations.pdf}

\begin{figure}[!ht]
  \centering
  \includegraphics[width=\textwidth]{figures/fig-bgs-covars-with-fixations.pdf}
